Modelling the gas kinematics of an atypical Lyman alpha emitting compact dwarf galaxy

### 2017-06-25 paper/paper.tex
revised rotation model

Figure \ref{fig:tree} shows the results for one of such tree. 
Starting with $28$ and $1962$ models in the low and high
$\chi^2/d.o.f.$ classes respectively, we find that the best separation
yields $13$ and $44$ models after selecting for $v_{\infty,{\rm cl}}<157.0$ \kms,
$\sigma_{{\rm cl}}>55.6$ \kms and $P_{\rm cl}>0.683$.
The split is not perfect. This means that the three parameters in the
model are the most influential, but that some combinations of the
other 11 parameters are also relevant to find a good fit.

@@

Qualitatively this result can be understood as follows. 
The broad \lya\ line is the result of subsequent \lya\ photon
scatterings due to (relatively) fast moving clumps while the
multi-phase nature (i.e., the existence of low-density inter-clump
regions where \lya\ photons can freely prograpagate)  ensures the high
flux at line center as observed.   
In turn, a lower velocity dispersion would produce a thiner line than
it is observed.
From the lower right panel in Figure \ref{multiphaseresults} we find that it
is unlikely that the clump velocity dispersion is lower than
$50$\kms.

@@

The results are summarized in  Figure \ref{emceeresults}. 
From this analysis we find that the best parameters in the rotation
model are a rotational velocity of  $V_{\rm max}=348^{+75}_{-48}$
\kms, a neutral Hydrogen optical depth of
$\log_{10}\tau=6.96^{+0.26}_{-0.18}$,  and an inter-stellar medium
temperature of $\log_{10} T/\mathrm {K} = 4.27^{+0.11}_{-0.18}$.   
We are also able to constrain the angle between the plane
perpendicular to the rotation axis and the observational line-of-sight
to $\theta = 35.78^{+2.13}_{-1.88}$ degrees.

Lower rotational velocities than the favored value would produce a
double peaked line as the different doppler shifts produced on
different regions of the rotating sphere would not be large enough to
smear the double peaks into a single peak
\citep{GaravitoCamargo2014}. 
For the same reason, higher rotation velocities could produce a single
peak but the line would be broader than it is observed.
The fact that the velocity and optical depth priors were wide enough,
allows us to suggest that the current values for the spherical model
found by the MCMC are robust given the observational constraints.

>>>>

Figure \ref{fig:tree} shows as an illustriation the results for one of such tree. 
Starting with $28$ and $1962$ models in the low and high
$\chi^2/d.o.f.$ classes respectively, we find that the best separation
yields $13$ and $44$ models after selecting for $v_{\infty,{\rm cl}}<157.0$ \kms,
$\sigma_{{\rm cl}}>55.6$ \kms and $P_{\rm cl}>0.683$.
The split is not perfect. This means that the three parameters in the
model are the most influential, but that some combinations of the
other 11 parameters are also relevant to find a good fit.

@@

Qualitatively this result can be understood as follows. 
The broad \lya\ line is the result of subsequent \lya\ photon
scatterings due to (relatively) fast moving clumps while the
multi-phase nature (i.e., the existence of low-density inter-clump
regions where \lya\ photons can freely prograpagate)  ensures the high
flux at line center as observed.   
In turn, a lower velocity dispersion would produce a thiner line than
it is observed.
From the lower right panel in Figure \ref{multiphaseresults} we find that it
is unlikely that the clump velocity dispersion is lower than
$50$\kms. 
This is also supported by the classification tree example in Figure
\ref{fig:tree}.

@@

The results for this model are easier to interpret due to the fewer
number of free parameters and its explicit influence on the
semi-analytic solution.
The results are summarized in  Figure \ref{emceeresults}. 
From this analysis we find that the best parameters in the rotation
model are a rotational velocity of  $V_{\rm max}=348^{+75}_{-48}$
\kms, a neutral Hydrogen optical depth of
$\log_{10}\tau=6.96^{+0.26}_{-0.18}$,  and an inter-stellar medium
temperature of $\log_{10} T/\mathrm {K} = 4.27^{+0.11}_{-0.18}$.   
We are also able to constrain the angle between the plane
perpendicular to the rotation axis and the observational line-of-sight
to $\theta = 35.78^{+2.13}_{-1.88}$ degrees.
This model cannot reproduce the slight asymmetry present in \tol's
\lya\ line; most probably this would require an small amount of
outflows, a feature that is not present in the model provided by
\cite{GaravitoCamargo2014}.

The prefered value for the rotational velocity can be explained as
follows. 
Lower rotational velocities than the favored value would produce a
double peaked line as the different doppler shifts produced on
different regions of the rotating sphere would not be large enough to
smear the double peaks into a single peak
\citep{GaravitoCamargo2014}. 
For the same reason, higher rotation velocities could produce a single
peak but the line would be broader than it is observed.
The fact that the velocity and optical depth priors were wide enough,
allows us to suggest that the current values for the spherical model
found by the MCMC are robust given the observational constraints.
